### 2021-05-01 sections/queueing_model/main.tex
Fix typo
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

The model consists of two types of individuals; class 1 and class 2.
Class 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
receive their service. 
Class 2 individuals arrive at waiting zone 2 and wait there until they are 
allowed to move to waiting zone 1. 
They are allowed to proceed to the next waiting zone only when the number of 
individuals in the next system (in waiting zone 1 and in service) is less than a 
pre-determined threshold \(T\).
When the threshold is reached, all class 2 individuals that arrive will remain 
\textit{``blocked''} in the buffer centre until the number of people in the 
system is reduced below \(T\). 
This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.
The parameters of the described queueing model are:

\begin{itemize}
    \item \(\lambda_1\): The arrival rate of class 1 individuals
    \item \(\lambda_2\): The arrival rate of class 2 individuals
    \item \(\mu\): The service rate for individuals receiving service in waiting 
    zone 1
    \item \(C\): The number of servers
    \item \(T\): The threshold where class 2 individuals will start being blocked 
\end{itemize}

@@

\begin{itemize}
    \item \(u\) = number of individuals blocked
    \item \(v\) = number of individuals either in waiting zone 1 or in the
    service centre
\end{itemize}

@@

\input{sections/queueing_model/general-markov-model/main.tex}

>>>>

The model consists of two types of individuals; class 1 and class 2.
Class 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
receive their service. 
Class 2 individuals arrive at waiting zone 2 and wait there until they are 
allowed to move to waiting zone 1. 
They are allowed to proceed only when the number of 
individuals in waiting zone 1 \textbf{and} in service is less than a 
pre-determined threshold \(T\).
When the number of individuals is equal to or exceeds this threshold, all second type individuals that arrive will remain 
\textit{``blocked''} in waiting zone 1 until the number of people in the 
system is reduced below \(T\). 
This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.
The parameters of the described queueing model are:

\begin{itemize}
    \item \(\lambda_i\): The arrival rate of individuals of type \(i\in\{1, 2\}\)
    \item \(\mu\): The service rate for individuals receiving service
    \item \(C\): The number of servers
    \item \(T\): The threshold at which individuals of the second type are blocked
\end{itemize}

@@

\begin{itemize}
    \item \(u\) is the number of individuals blocked
    \item \(v\) is the number of individuals either in waiting zone 1 or in the
    service centre
\end{itemize}

@@

\input{sections/queueing_model/general_markov_model/main.tex}
